article title

### 2024-09-12 article.tex
Add fontenc for 8 bit fonts 256 glyphs
Edit comment re fontenc
Add glossary term machineleaning
Add gls terms
Edit content

@@

% useful for the glossary
\usepackage[toc, acronym, nopostdot, numberedsection, record=hybrid, shortcuts=ac, abbreviations]{glossaries-extra}
\makeglossaries
\GlsXtrLoadResources[
    src={pilon_gilles_glossary.bib},
    selection={recorded and deps},
    sort=letter-nocase
]

@@

The author wishes to thank ...

@@

Here is a single citation with postnote only. $C_\text{pm}$ is a complex subject (\cite[][pages 1-10]{chan1988}).

@@

Here is a request to fill in \gls{endog}, \glspl{endog}, \gls{exog}, and \glspl{exog}.

For dual abbreviations and glossary terms, \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, and \gls{anome}.

>>>>

% required for 8 bit fonts 256 glyphs
\usepackage[T1]{fontenc}

@@

% useful for the glossary
\usepackage[toc, nopostdot, numberedsection, record=hybrid, shortcuts=ac, abbreviations]{glossaries-extra}
\makeglossaries
\GlsXtrLoadResources[
    src={~/documents/repositories/latex/pilon_gilles_glossary.bib},
    selection={recorded and deps},
    sort=letter-nocase,
    selection={all} % shows all glossary entries
]

@@

The author wishes to thank ... \LaTeX and \LaTeXe

@@

Here is a single citation with postnote only. $C_\text{pm}$ is a complex subject (\cite[][1-10]{chan1988}).

@@

Here is a request to fill in \gls{endog}, \glspl{endog}, \gls{exog}, \glspl{exog}, \gls{machinelearning}, and \gls{seborrheickeratosis}.

For dual abbreviations and glossary terms, \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, \gls{anome}, \gls{iam}, \gls{pam}, \gls{edr}, \glsxtrlong{xdr}, \gls{pythonnamespace}, \gls{cybersecurity}.
